---
title: "Gun Control Chi-Square"
author: "Tara Jagadeesh"
date: "November 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This: I'm Tara and I'm updating this markdown file here. 


```{r}
library(tidyverse)
gcdf <- read_csv("gc_df.csv")

```

We are asking: Is there a significant difference in recommended gun control action between male and female respondents (should guns be easier, harder, or same difficulty to get)?

Tara: data wrangling and counts

```{r}
get_guns <- gcdf %>% 
  filter(gender != "NA", make_get_guns != "NA") %>% 
  count(gender, make_get_guns) %>% 
  spread(make_get_guns, n) %>% 
  select(-gender)

rownames(get_guns) <- c("Female","Male")
```

My name is Sandro the collaborator and I'm going to be doing chi-square test for independence!

We ask: "Is there a significant association between sex and opinion on whether guns should be more difficult, easier, or the same difficulty to get?"

```{r}

# Let's look at the actual proportions:

guns_prop <- prop.table(as.matrix(get_guns), 1)

guns_prop

# Run chi-square test for independence

guns_x2 <- chisq.test(get_guns)

guns_x2

```

"Recommended government action on gun access differed significantly between male (n = ) and female (n = ) respondents ($\chi^2$(`r guns_x2$parameter`) =...., p < 0.001). Notably, a much higher proportion of female respondents (57.4%) recommend making it more difficult to get guns, compared to 40.4% for male respondents."
